Polyglots: Crossing Origins by Crossing Formats

### 2013-08-11 rebuttal.txt

As for other vulnerable formats, future work mentions scriptable media formats, e.g.,
Advanced Streaming Format (ASF), as another problem area. However, space constraints
prohibits us from further exploring these formats within the scope of this paper.

Advanced mitigation:

We are convinced the mitigation techniques we suggest are both most needed and
realistically deployable. Regarding more advanced defenses, we will be happy to include in
the paper a discussion of most promising directions. For example, note that when content
is loaded in a specific context, as it is in the case of the paper, the browser already
has exact knowledge as to what type it will interpret the requested content as. A natural
defense technique can be to send the expected type along with the request. The web server
then can compare the types and react accordingly. Further, it can be implemented in the
web server itself (as opposed to the web application), since the web server makes the
final decision on the supplied content-type. This cooperation between client and server
can help mitigate both syntax injection and content smuggling.

Evaluation of mobile browsers would indeed make an interesting topic for future work.

@@

Concerning XML External Entities (XXE) in Adobe Reader, the problem of XXE was previously known 
(since ca. 2005), but considered to be of low priority. Our reports may have influenced Adobe's 
decision to finally remove them, but it is not known to us to what extent.

We plan to make the treatment of the related work more coherent. Also, we are happy to
follow the suggestion to update the visualization with a more professional appearance, to
move the listings to their appropriate positions and generally clarify the exposition,
where appropriate.

### 2013-08-11 main.tex

\paragraph{Classical cross-domain attacks}
There are several classes of cross-domain attacks that circumvent SOP.
The OWASP top 10 list~\cite{OWASP:top10:2010} places \emph{injection}
and \emph{cross-site scripting} (XSS) attacks as two top security
risks for web applications.
%
A classical XSS attack injects a malicious script in the context of a
trusted origin. This opens up opportunities for leaking sensitive
information that users might have in the context of the trusted origin
such as cookies, personal information, and session tokens.

XSS attacks are relatively well understood by researchers and
developers~\cite{XSSED}. Known defense include various
flavors of \emph{sanitization} on server side and the
\emph{content security policy}~\cite{CSP1.0} (CSP) on client side. Sanitization
is often performed by the server to filter possibly malicious input data
before it is used in the generated web pages. Content security policy puts
requirement on the structure of the document and the origins of the
scripts that are included by web pages.

\paragraph{Crossing origins by crossing formats}
This paper identifies a new breed of attacks and its root cause:
\emph{polyglots}. 
%
A polyglot is a program that is valid in multiple programming languages.
%
In a heterogeneous system like the web, information is exchanged
between components in versatile formats.
%
This gives rise to attacks that exploit the mismatch between the
expected and provided content.
%
Polyglots allow
multiple interpretation of the content, providing a new space of attack vectors.
An attacker can use a polyglot to infiltrate a vulnerable origin.
Once infiltrated, the polyglot is embedded in the attackers web site using a plug-in.
According to the SOP, content loaded in a plug-in is considered to belong to the 
origin from which the content was requested, thus allowing the polyglot to communicate with the vulnerable 
origin. A victim visiting the attacker's web site, while authenticated in the vulnerable
origin, will activate the malicious polyglot, which can abuse the credentials of the victim 
in its communication with the vulnerable service. The scenario is explained in detail in Section~\ref{sec:vectors},
where we present novel attack vectors that are based on (i)
\emph{syntax injection} that 
operate across multiple languages and on (ii) \emph{content smuggling} that supply
malicious payload that appears formatted as benign content. The
attacks lead to both \emph{cross-domain leakage} and \emph{cross-site
request forgery}.

>>>>

\paragraph{Classical cross-domain attacks}
There are several classes of cross-domain attacks that circumvent SOP.
The OWASP top 10 list~\cite{OWASP:top10:2013} places both \emph{injection}
and \emph{cross-site scripting} (XSS) attacks among the three top security
risks for web applications.
%
A classical XSS attack injects a malicious script in the context of a
trusted origin. This opens up opportunities for leaking sensitive
information that users might have in the context of the trusted origin
such as cookies, personal information, and session tokens.

XSS attacks are relatively well understood by researchers and
developers~\cite{XSSED}. Known defenses include various
flavors of \emph{sanitization} on server side and the
\emph{content security policy}~\cite{CSP1.0} (CSP) on client side. Sanitization
is often performed by the server to filter possibly malicious input data
before it is used in the generated web pages. Content security policy puts
requirement on the structure of the document and the origins of the
scripts that are included by web pages.

\paragraph{Crossing origins by crossing formats}
This paper identifies a new breed of attacks and its root cause:
\emph{polyglots}. 
%
A polyglot is a program that is valid in multiple programming languages.
%
In a heterogeneous system like the web, information is exchanged
between components in versatile formats.
%
This gives rise to attacks that exploit the mismatch between the
expected and provided content.
%
Polyglots allow
multiple interpretation of the content, providing a new space of attack vectors.
An attacker can use a polyglot to infiltrate a vulnerable origin.
Once infiltrated, the polyglot is embedded from within the attacker's web site,
so that the polyglot is loaded in the browser's plug-in.
According to the SOP, content loaded in a plug-in is considered to belong to the 
origin from which the content was requested, thus allowing the polyglot to communicate with the vulnerable 
origin. A victim visiting the attacker's web site, while authenticated in the vulnerable
origin, will activate the malicious polyglot, which can abuse the credentials of the victim 
in its communication with the vulnerable service. The scenario is explained in detail in Section~\ref{sec:vectors},
where we present novel attack vectors that are based on (i)
\emph{syntax injection} that 
operate across multiple languages and on (ii) \emph{content smuggling} that supply
malicious payload that appears formatted as benign content. The
attacks lead to both \emph{cross-domain leakage} and \emph{cross-site
request forgery}.
